Towards Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision

### 2018-07-02 SWoPP2018 Paper/paper.tex
Small additions.

\subsection{Network Tested + Data-set}
The used example network is a simple multilayer perceptron.
The first data set used was MNIST, so \num{784} input features.
The structure of the sample MNIST network is.
\begin{enumerate}
  \item Dense(512)  \(\to\)  Relu
  \item Dense(512)  \(\to\)  Relu
  \item Dense(10)  \(\to\)  Softmax
\end{enumerate}
So in total a three layer network, or threes sets of weight matrices and bias vectors.
The data set was trained using the first \num{60000} images from the MNIST data set.
The last \num{10000} images are used as the test data set.
The second data set used was CIFAR10, so \num{3072} input features.
The structure of the sample CIFAR10 network is.
\begin{enumerate}
  \item Dense(1024)  \(\to\)  Relu
  \item Dense(512)  \(\to\)  Relu
  \item Dense(512)  \(\to\)  Relu
  \item Dense(10)  \(\to\)  Softmax
\end{enumerate}

>>>>

\subsection{Network Tested + Data-set}
The used example networks are a simple multi-layer perceptron.
So all layers are a simple array neurons and every neuron is connected to every neuron in the next layer.
These layers are often called ``Dense'' layers.
The first data set used was MNIST, MNIST is a collection of 28\(\times\)28 gray scale images of hand written arabic numerals.
So the data set provides \num{784} input features.
The structure of the sample MNIST network is.
\begin{enumerate}
  \item Dense(512)  \(\to\)  Relu
  \item Dense(512)  \(\to\)  Relu
  \item Dense(10)  \(\to\)  Softmax
\end{enumerate}
So in total a three layer network, or threes sets of weight matrices and bias vectors.
The data set was trained using the first \num{60000} images from the MNIST data set.
The last \num{10000} images are used as the test data set.
The second data set used was CIFAR10, so \num{3072} input features.
The structure of the sample CIFAR10 network is.
\begin{enumerate}
  \item Dense(1024)  \(\to\)  Relu
  \item Dense(512)  \(\to\)  Relu
  \item Dense(512)  \(\to\)  Relu
  \item Dense(10)  \(\to\)  Softmax
\end{enumerate}
